	%% start of file `template_en.tex'.
%% Copyright 2007 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper]{moderncv}
\usepackage[latin1]{inputenc}
\usepackage{url}



% moderncv themes
%\moderncvtheme[blue]{casual}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
\moderncvtheme[green]{classic}                % idem

% character encoding
%\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{\huge Susy}
\small \familyname{\huge Echeverr\'ia-Londo\~no, PhD. }
\title{NSF Postdoctoral Associate}               % optional, remove the line if not wanted
\address{\hspace{-1in}Kenyon College}{Department of Biology}{OH 43022}    % optional, remove the line if not wanted
\mobile{+1(740)5046838}                    % optional, remove the line if not wanted
%\phone{+5776348129}                      % optional, remove the line if not wanted
%\fax{312 996 1491}                          % optional, remove the line if not wanted
\email{susyelo@gmail.com}
                    % optional, remove the line if not wanted
\extrainfo{echeverrialondono1@kenyon.edu} % optional, remove the line if not wanted
%\photo[64pt]{./cv.jpg}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{"No man should escape our universities without knowing how little he knows." -- J. Robert Oppenheimer}                 % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

\newcommand{\cvreference}[7]{%
    \textbf{#1}\newline% Name
    \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
    \ifthenelse{\equal{#3}{}}{}{#3\newline}%
    \ifthenelse{\equal{#4}{}}{}{#4\newline}%
    \ifthenelse{\equal{#5}{}}{}{#5\newline}%
    \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
    \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{RESEARCH INTERESTS}

I aim to understand large-scale patterns of biodiversity and the ecological and evolutionary processes that shaped them. I am also interested in understanding how human pressures have affected and will affect the biodiversity in tropical regions, and consequences of the homogenization of assemblages. 

\section{EDUCATION}

\cventry{2018--}{Visitor scholar}{University of Pittsburgh}{\textit{Department of Biological Science}}{Pittsburgh, PA 15260, United States of America}{}
\cvline{}{PI: Prof. Justin Kitzes}

\cventry{2017--}{NSF Postdoctoral Associate}{Kenyon College}{\textit{Department of Biology}}{Gambier, OH 43022, United States of America}{}
\cvline{}{PIs: Prof. Andrew Kerkhoff and Prof. Brian J Enquist}

\cventry{2013--2017}{PhD in Life Science}{Imperial College London}{\textit{Natural History Museum}}{Cromwell Rd, London SW7 5BD, United Kingdom}{}

\cvline{}{\textbf{Thesis:} Diversification patterns of \textit{Solanum} L. (Solanaceae), plant macroecology and responses to land-use change}
\cvline{}{Supervisor: Prof. Andy Purvis; Co-supervisor Dr Sandra Knapp}

\cventry{2012--2013}{MRes (Distinction) in Biodiversity Informatics and Genomics}{Imperial College London}{Silwood Park, SL5 7PY}{United Kingdom}{}

%\cvline{}{\textbf{Thesis:} Modelling and projecting response of Colombian biodiversity to land-use change}
%\cvline{}{Supervisor: Prof. Andy Purvis}


\cventry{2004--2010}{BSc (Hons) in Biology}{Universidad Industrial de Santander}{Bucaramanga}{Colombia}{}
%\cvline{}{Grade point average, 4.2/5.0}
%\cvline{}{\textbf{Thesis:} A geometrical approach for identifying geographical patterns of distribution.}
%\cvline{}{Supervisor: Dr Daniel Rafael Miranda-Esquivel}


\section{PUBLICATIONS}

\cvline{In prep}{\textbf{Echeverr\'ia-Londo\~no S.}, Neves, DM. , Kerkhoff, AJ, Enquist, BJ. Evolutionary biome shifts of angiosperms in the New World}

\cvline{In prep}{Neves, DM. , Kerkhoff, AJ, \textbf{Echeverr\'ia-Londo\~no S.}, Enquist, BJ. The evolutionary history of New World biomes}

\cvline{In prep}{\textbf{Echeverr\'ia-Londo\~no S.,} De Palma, A., Contu, S., Hill, S. L., Lysenko, I., Knapp, S., and Purvis, A. Plant species' responses to land-use change: A global perspective}

\cvline{2018}{\textbf{Echeverr\'ia-Londo\~no S.,} Enquist, BJ, Neves, DM, Violle, C and Kerkhoff, AJ.  Plant functional diversity and the biogeography of biomes in North and South America, Frontiers in Ecology and Evolution, 6(DEC), 219}

\cvline{2018}{\textbf{Echeverr\'ia-Londo\~no S,.}  S{\"a}rkinen, T., Fenton, I. S., Knapp, S., \& Purvis, A. Dynamism and context dependency in the diversification of the megadiverse plant genus Solanum L.(Solanaceae). bioRxiv, 348961.}

\cvline{2017}{Isaacs, P., \textbf{Echeverr\'ia-Londo\~no, S.,} Urbina, N and Purvis, A. Species Composition and Changes in Land Use: considerations under climatic change scenarios. Moreno, L. A., Andrade, G. I. and Ru\'iz-Contreras, L. F. (Ed.)  In \textit{Biodiversity 2016. Status and Trends of Colombian Continental Biodiversity}. Instituto de Investigaci\'on de Recursos Biol\'ogicos Alexander von Humboldt, 106 p}

\cvline{2017}{Hudson, L. N., Newbold, T., Contu, S., Hill, S. L., Lysenko, I., De Palma, A., Diaz, S., \textbf{Echeverr\'ia-Londo\~no S,.} ... \& Purvis. The database of the Predicts (Projecting responses of ecological diversity in changing terrestrial systems) project. Ecology and Evolution, 7(1), 145-188.}

\cvline{2016}{\textbf{Echeverr\'ia-Londo\~no S.,} Newbold, T., Hudson, L. N., Hill, S. L., Contu, S., Lysenko, I., ... \& Purvis, A. Modelling and projecting the response of Colombian biodiversity to land-use change. Diversity and Distributions, 22: 1099-1111, doi:10.1111/ddi.12478. }

\cvline{2015}{Newbold, T., Hudson, L. N., Hill, S. L., Contu, S., Lysenko, I., Senior, R. A., Bennet D. J., Choimes A., Collen, B., Day, J., De Palma, A., Diaz, S., \textbf{Echeverr\'ia-Londo\~no S,.} ... \& Purvis, A. Global effects of land use on local terrestrial biodiversity. Nature, 520(7545), 45-50.}

\cvline{2014}{Newbold, T., Hudson, L. N., Contu, S.,  Hill, S. L., Lysenko, I., De Palma, A., Phillips, H., Senior, R. A., Bennet D. J., Booth, H., Choimes A., Correia, D. L. P., Day, J, \textbf{Echeverr\'ia-Londo\~no S,.} ... \& Purvis, A. The PREDICTS database: a global database of how local terrestrial biodiversity responds to human impacts. Ecology and evolution 4.24: 4701-4735. }

\cvline{2011}{\textbf{Echeverr\'ia-Londo\~no, S }\& Miranda-Esquivel, D. R. MartiTracks: A geometrical approach for identifying geographical patterns of distribution. PLoS ONE 6(4): e18460. doi:10.1371/journal.pone.0018460 \url{http://dx.plos.org/10.1371/journal.pone.0018460}}

\cvline{2010}{Miranda-Esquivel, D. R, Morales-Guerrero, A. M \& \textbf{Echeverr\'ia-Londo\~no S.} \textquestiondown Cu\'antos somos? y \textquestiondown C\'omo nos cuantificamos?. Book chapter. Evoluci\'on "Historia de la Vida". Asociaci\'on Colombiana para el avance de la Ciencia ACAC.}


\section{INTERNATIONAL CONFERENCE PRESENTATIONS}

\cvline{2018}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S, et al. Explosive diversification of \textit{Solanum} L (Solanaceae) in the old world. \textbf{Three Rivers Evolution meeting}, Pittsburgh, Pennsylvania, USA}

\cvline{2018}{\textbf{Poster:} Echeverr\'ia-Londo\~no S, et al. Plant functional diversity and the biogeography of biomes in North and South America. \textbf{Three Rivers Evolution meeting}, Pittsburgh, Pennsylvania, USA}

\cvline{2018}{\textbf{Poster:} Echeverr\'ia-Londo\~no S, et al. Plant functional diversity and the biogeography of biomes in North and South America. \textbf{Botany 2018}, Rochester, Minnesota, USA}

\cvline{2016}{\textbf{VVIP Presentation:} Echeverr\'ia-Londo\~no S, et al. Modelling and projecting the response of Colombian biodiversity to land-use change. \textbf{State visit by the President of Colombia, Juan Manuel Santos, to the UK and the Prince of Wales}. Natural History Museum, London, United Kingdom}

\cvline{2016}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S, et al. Modelling and projecting the response of Colombian biodiversity to land-use change. \textbf{First symposium of Colombian research in the UK}. Imperial College London, London, United Kingdom}

\cvline{2016}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S, Knapp S. \& Purvis A. Explosive diversification of \textit{Solanum} L (Solanaceae) in the old world. \textbf{BES macroecology meeting 2016}. Oxford University, Oxford, United Kingdom}

\cvline{2016}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S, Knapp S. \& Purvis A. Diversification patterns of genus \textit{Solanum}. \textbf{NHM students conference 2016}. Natural History Museum, London, United Kingdom}

\cvline{2015}{\textbf{Poster:} Echeverr\'ia-Londo\~no S, Knapp S. \& Purvis A. Explosive diversification of \textit{Solanum} L (Solanaceae) in the old world. \textbf{Systematics: The Science that Underpins Biology. The Systematic Association Biennal meeting}, Oxford University, Oxford, United Kingdom}

\cvline{2015}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S, Knapp S. \& Purvis A. Explosive diversification of \textit{Solanum} L (Solanaceae) in the old world. \textbf{EU Macroecology meeting}. Zoological museum of Copenhagen, Copenhagen, Denmark}

\cvline{2015}{\textbf{Poster:} Echeverr\'ia-Londo\~no S, Knapp S \& Purvis A. Diversification patterns of \textit{Solanum}. \textbf{NHM students conference 2015}. Natural History Museum, London, United Kingdom}

\cvline{2014}{\textbf{Poster:} Echeverr\'ia-Londo\~no S, Knapp S \& Purvis A. Diversification patterns of \textit{Solanum}. \textbf{The London Evolutionary Research Network (LERN)}. Queen Mary University, London, United Kingdom}

\cvline{2014}{\textbf{Poster:} Echeverr\'ia-Londo\~no S, Knapp S \& Purvis A. Patterns of lineage diversification in the genus Solanum L. \textbf{Plants Radiation meeting}. Institute of Systematic Botany, University of Z\"urich, Switzerland.}

\cvline{2013}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S, \textit{et al.,} Modelling and projecting the responses of Colombian biodiversity to human impacts. \textbf{11th INTECOL Conference, Ecology}, London, United Kingdom.}

\cvline{2010}{\textbf{Presentation:} Echeverr\'ia-Londo\~no S \& Miranda-Esquivel D. M. Panbiogeograf\'ia cuantitativa: un acercamiento geom\'etrico. \textbf{III Congreso Colombiano de Zoolog\'ia.} Medell\'in, Colombia.}

\cvline{2009}{\textbf{Presentation:} Miranda-Esquivel D. M, Echeverr\'ia-Londo\~no S. \& Morales-Guerrero A. M. Todas las secuencias son iguales, pero unas son mas iguales que otras. \textbf{III Simposio red colombiana de Biolog\'ia Evolutiva.-Colevol-} Cali, Colombia.}


\section{INVITED SEMINARS}

\cvline{2018}{Ecology and Evolution seminars, Department of Biological Sciences, University of Pittsburgh, USA.}

\cvline{2017}{Department of Biology seminars, Kenyon College, USA.}

\cvline{2017}{Ecosystems and Tropical Forest group lab seminar,  School of Geography and the Environment, University of Oxford, UK.}

\cvline{2015}{Ecology and Evolution seminar, Royal Botanic Garden Edinburgh, UK.}


\section{AWARDS AND RECOGNITIONS}

\cvline{2018}{NSF grant fund ``RCN-UBE Incubator: The Biological and Environmental Data Education Network'', \$ 72,361}

\cvline{2016}{Selected to present research to the (Nobel Peace Prize-winning) President of Colombia and His Royal Highness the Prince of Wales. Natural History Museum, London, UK}

\cvline{2013}{Distinction in MRes in Biodiversity Informatics and Genomics. Imperial College London. Silwood Park Campus, UK}

\cvline{2004--2009}{Academic Stimuli. First place (Highest GPA) in I, II, IV, IX semester. Academic program of Biology. Universidad Industrial de Santander, Bucaramanga, Colombia}

\section{RESEARCH SCHOLARSHIPS}

\cvline{2012-2016}{Postgraduate scholarship. Administrative Department of Science, Technology and Innovation  of Colombia (Colciencias). $\pounds$ 122,000}
\cvline{2013}{Training and travel grant. British Ecology Society (BES): $\pounds$300}
\cvline{2013}{Bursary. MRes in Biodiversity Informatics and Genomics. Imperial College London. Silwood Park Campus: $\pounds$1,000}


\section{TEACHING EXPERIENCE}

%\cventry{2012-2013}{PREDICTS team member}{Imperial College London}{Silwood park}{United Kingdom}{Projecting Responses of Ecological Diversity In Changing Terrestrial Systems (PREDICTS) project \url{http://www.predicts.org.uk/team.html}}

\cventry{2017-2018}{Course Coordinator}{Global Ecology and Biogeography and Ecoinformatics, Kenyon College London}{Gambier, OH}{USA}{}

\cventry{2017}{Lecturer}{MSc Taxonomy and biodiversity, Methods in Macroecology and Macroevolution course, Natural History Museum (NHM) and Imperial College London }{London}{UK}{Phylogenetic approaches to studying diversification}

\cventry{2017}{Demonstrator}{MSc Taxonomy and biodiversity, Natural History Museum (NHM) and Imperial College London }{London}{UK}{Fossils in phylogenetics}

\cventry{2013-2016}{Demonstrator}{Computational Biostatistics BSc course, Ecology and Evolution BSc course, Biodiversity and Conservation Biology BSc course, Imperial College London}{London}{UK}{Fundamentals of statistics, Describing data, $t$ and $F$ tests, Linear regression, ANOVA, Count data, $\chi^2$ tests, Phylogeny of mammals and pines, IUCN Red List, R basics, Biodiversity among lineages and over time, Delimiting species, Extinction risk patterns and correlates}

%\cventry{2015}{Demonstrating}{Ecology and Evolution BSc course, Imperial College London}{London}{UK}{Phylogeny of mammals and pines}
%
%\cventry{2014}{Demonstrating}{Biodiversity and Conservation Biology BSc course, Imperial College London}{London}{UK}{IUCN Red List}
%
%\cventry{2013}{Demonstrating}{Biodiversity and Conservation Biology BSc course, Imperial College London}{London}{UK}{R basics, Biodiversity among lineages and over time practical, Delimiting species, Extinction risk patterns and correlates}

\cventry{2012}{Science teacher}{New Cambridge School}{Floridablanca}{Colombia}{}

\cventry{2012}{Science teacher}{Gimnasio pontevedra school}{Bucaramanga}{Colombia}{}

\cventry{2011}{Head of science department and teacher}{La Quinta del puente school}{Bucaramanga}{Colombia}{}

\cventry{2008--2010}{Teaching Assistant}{Systematics BSc course, Universidad Industrial de Santander}{Bucaramanga}{Colombia}{}
             
   % arguments 3 to 6 are optional
\cventry{2009}{Teaching Assistant}{Bioinformatics MSc course, Universidad Industrial de Santander}{Bucaramanga}{Colombia}{}
%Masters of Basic Biomedical Sciences Program                       % arguments 3 to 6 are optional
%\subsection{Miscellaneous}
%\cventry{year--year}{Job title}{Employer}{City}{}{Description line 1\newline{}Description line 2}% arguments 3 to 6 are optional

\section{SCIENCE OUTREACH}
\cvline{2014}{\textit{Science Uncovered at the Natural History Museum}. Presented the PREDICT project (\url{www.predicts.org.uk/}): Projecting Responses of Ecological Diversity In Changing Terrestrial Systems, and also the Solanaceae source project \url{www.solanaceaesource.org}}

\newpage

\section{NON-ACADEMIC SERVICES}

\cvline{2015--2016}{Secretary. Latin American Society, Imperial College London, London, UK. Responsible for running the fresher-fair, writing minutes and organizing dance sessions.}



%\section{Undergraduate Thesis}


%\section{Awards	}

%Academic Stimuli. First place (Highest GPA) in # semester. Academic Program of Biology. Universidad Industrial de Santander.


%\newpage



%\section{Postgraduate courses}
%
%\cvline{2013}{Postgraduate Course in C programming}
%\cvline{}{Imperial College London}
%
%\cvline{2009}{Introduction to evolutionary biogeography. Facultad de Ciencias Exactas y Naturales. Posgrado de Biolog\'ia. Universidad de Antioquia. Medell\'in, Colombia.}
%\cvline{supervisors}{Juan Jose Morrone Lupi, Tania Escalante Espinosa}


%\section{Other courses}
%
%\cvline{2011}{Introduction to web based programming (HTML and JAVASCRIPT). Servicio Nacional de Aprendizaje SENA}
%
%\cvline{2011}{Java applet development, events management, classes and objects. Servicio Nacional de Aprendizaje SENA.}
%
%\cvline{2011}{Modules, storage structures and OOP using C++ programming language( Level II). Servicio Nacional de Aprendizaje SENA.}
%
%\cvline{2010}{Structure oriented programming language C++ (Level I). Servicio Nacional de Aprendizaje SENA.}
%
%\cvline{2010}{Variables, and control structures in object oriented programming: JAVA. Servicio Nacional de Aprendizaje SENA.}



%\section{Training courses and workshops}
%
%\cvline{2014}{Plant taxonomy course. NERC-funded training courses. The Natural History Museum, London, United Kingdom}
%
%\cvline{2014}{Molecular techniques for taxonomy. NERC-funded training courses. The Natural History Museum, London, United Kingdom}
%
%\cvline{2014}{Radiation and extinction: Investigating clade dynamics in deep time workshop. The Linnean Society and Imperial College London, London, United Kingdom}
%
%\cvline{2014}{Phylogeny, extinction risks and conservation discussion meeting. The Royal Society, London, United Kingdom}
%
%\cvline{2013}{Spatial analysis in R. BES Macroecology SIG workshop. Sheffield University, Sheffield, United Kingdom}
%
%\cvline{2013}{Postgraduate course in C programming, Imperial College London, London, United Kingdom}
%
%\cvline{2013}{The generalised linear modelling (GLIM) course presented by Prof. M. J. Crawley, Imperial College London, London, United Kingdom}
%
%\cvline{2009}{Introduction to evolutionary biogeography. Facultad de Ciencias Exactas y Naturales. Posgrado de Biolog\'ia. Universidad de Antioquia. Medell\'in, Colombia.}

\small
\section{COMPUTER SKILLS}
\cvcomputer{OS}{Linux/Unix, Windows, OS X}{}{}
\cvcomputer{Programming}{R, Python, Basic C++, shell, basic HPC cluster scripts}{}{} 
\cvcomputer{Version control}{Git}{}{} 
\cvcomputer{Typography}{\LaTeX, OpenOffice/LibreOffice}{}{}
%\cvcomputer{Phylogeny software}{POY, TNT, Nona, Winclada, PhyML, MrBayes, Bioedit, PAUP, R, BAMM}{}{}
%\cvcomputer{Biogeography software}{BioGeoBears, NDM, VNDM, Component 1.5, Component 2, DIVA, TREEFITTER, Martitracks}{}{}


\section{LANGUAGES}
\cvline{Spanish}{Native}
\cvline{English}{Proficient}
\cvline{Italian}{Intermediate}



%\cvline{2015}{International development conference (IDC). Imperial College London, London, United Kingdom}
%
%\cvline{2014}{16th Young Systematists' forum. Natural History Museum, London, United Kingdom}
%
%
%
%\cvline{2014}{Plants Radiation meeting. Institute of Systematic Botany, University of Z\"urich, Switzerland}
%
%\cvline{2013}{11th INTECOL Congress, Ecology, London, United Kingdom}
%
%\cvline{2010}{III Congreso Colombiano de Zoolog\'ia. Medell\'in, Colombia.}
%\cvline{2009}{III Simposio red colombiana de Biolog\'ia Evolutiva.-Colevol-. Cali-Colombia}
%\cvline{2007}{V Congreso Internacional y VIII Congreso Colombiano de Gen\'etica. Cali, Colombia.}
%\cvline{2007}{I Congreso Nacional de Estudiantes de Biolog\'ia. Bogot\'a. Colombia.}
%\cvline{2006}{IV Congreso Internacional y VII Congreso Colombiano de Gen\'etica.  Bucaramanga, Colombia.}
%
%\section{\textbf{Languages}}
%\cvlanguage{2012}{Pre-sessional course in English.}{Level of competence in English: 7.0 \\ University of Bath}

%\cvlanguage{2011}{TOEFL IBT}{
%Score 98/120\\
%Reading score: 29\\
%Listening score: 25\\
%Speaking score: 23\\
%Writing score: 21\\
%ETS ID:	5653379\\
%Registration Number: 0000000013635906\\
%Date of examination: 17-Dec-2011
%}
%\cvlanguage{2010}{Michigan English Test}{Score 127}

\section{References}

\vspace{0.3cm}

\cvreference{Prof Andrew J. Kerkhoff}
{Professor of Biology}
{Department of Biology}
{Kenyon College}
{Higley Hall, Gambier, OH 43022}
{+1 740 427 5734}
{kerkhoffa@kenyon.edu}%

\vspace{0.5cm}
    
\cvreference{Prof Andy Purvis}
 	{Research Leader}
    {Department of Life Science}
    {Natural History Museum and Imperial College London}
    {Cromwell Rd, Kensington, London SW7 5BD}
    {Andy.Purvis@nhm.ac.uk}
    {+44 020 7942 5686}%
    
    \vspace{0.5cm}
    
\cvreference{Dr Sandra Knapp}
    {Merit Researcher, Head of Division}
    {Department of Life Science}
    {Natural History Museum}
    {Cromwell Rd, Kensington, London SW7 5BD}
    {+44 020 7942 5171}
    {s.knapp@nhm.ac.uk}%
    
      \vspace{0.5cm}
    


\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem[+]{Item 3}            % optional other symbol

%\section{Extra 2}
%\cvlistdoubleitem[\Neutral]{Item 1}{Item 4}
%\cvlistdoubleitem[\Neutral]{Item 2}{Item 5}
%cvlistdoubleitem[\Neutral]{Item 3}{}

% Publications from a BibTeX file
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{publications}       % 'publications' is the name of a BibTeX file

\end{document}


%% end of file `template_en.tex'.